\documentclass[10pt, twocolumn] {IEEEtran}
\usepackage{verbatim}
\usepackage{graphicx}

\newcommand{\myscale}{0.65}
\renewcommand{\baselinestretch}{0.960}

\begin{document}
\title{Title}
\author{Nutcha Chayanurak}
\maketitle
\begin{abstract} 
 \end{abstract}
\section{Introduction}
Heat transfer process is important for phase transition, such as ice melting and water freezing. Exemple, ice exchange heat with air surroundings. Surface of ice melt into a thin layer of water  gradually and enclose on ice when temperature of ice is equal melting point and heat of ice is equal latent heat. This porcess also occur in water freezing. In this paper, We propose a new approach based on 
a particle-based model for simulating ice melting and water freezing. 

In particle-based approach, an ice object and the water are represented by a set of particles. The phase transitions and the interaction between ice and water can be simulated by using our method. To simulate the melt water on ice surface and ice flake on water surface, the ice-water interface is represented by sparsely sampled particles.    

 
\section{Previous Work}
This section reviews previous concept to simulate ice-water interface for thermodynamic heat transfer process in freezing and melting phenomena. 

Ice-water interface in freezing simulation is a thin layer for connect between ice suface and water surface. Kim et al.\cite{kim2004hybrid} presented a hybrid algorithm for generating a thin ice crystal growth by the thermodynamics, such as snowflake. However this method cannot be applied on a volume of ice, such as icicles, and ice crystal generated from water vapor. Afterwards They was solving icicle formation by the thin-film Stefan problem for model a thin film of water\cite{kim2006modeling}. Madrazo et al. integrated air bubbles into ice\cite{madrazo2009air}. Their method simulated a dissolved air exhausted from ice-water interface to create geometrical representations of ice with bubbles.The interface moving is determined by a particle level set method, using the velocity field calculated by Stefan problem. However this paper studied only ice growth in bulk water case. Miao and Xiao\cite{Miao:2015:PIF:2817675.2817676} presented particle-based ice freezing model to simulate the fast freezing phenomenon occurs in flowing water. This method used surface particles of fluid to exchange heat with cold sources for various heat transfer directions can be controlled flexibly.
 
 In melting simulation, The ice-water interface is same in freezing but when rendering process it will be look like a water flow on ice surface. Iwasaki et al.\cite{iwasaki2010fast} proposed a Smoothed particle hydrodynamics (SPH) simulation method for the heat transfer in melting process. They improved a simple method for the interfacial forces between ice-water particle to simulate the flow of meltwater on ice and the formation of water droplets. Although this method can be applied to the simulation of water freezing, it was not further studied.
 Domaradzki and Martyn\cite{domaradzki2014improved} proposed new SPH air model represents the natural air convection on heat transfer process  which allows for considering  local changes in air temperature and a new external heat source model controls direction of melting.
 Lii and Wong\cite{lii2014ice} proposed new attribute called virtual water for ice particles. Their approach also handles the transition between the virtual water on ice surface and the water particles and computes the density field defined by the ice particles and the virtual water.
 
 Based on these two process, we make the following contributions to thin feature

\section{Method}
In this section, we propose new techniques to handle ice-water interface for SPH-based free surface flows.
\section{Result}
\section{Conclusion}
\section{Acknowledgement}

\nocite{*}
\bibliographystyle{unsrt}
\bibliography{BibFile}

\end{document}




